Rmarkdown Features

### 2018-03-22 DiagrammeR/rmd_features.rmd
update

#### Specific References
Include specific references, which are **not cited** in the body of text.
```{pandoc}
---
nocite: |
  @item1, @item2
...
```

#### All References
Include **All references** in the body of text.
```{pandoc}
---
nocite: |
  @*
...
```

>>>>

#### Specific Refs
Include specific references that were **not cited** in the body of text.
```{pandoc}
---
nocite: |
  @item1, @item2
...
```

#### All Refs
Include **All references** in the body of text.
```{pandoc}
---
nocite: |
  @*
...
```
